Constraining the Interiors of Asteroids Through Close Encounters

### 2022-04-26 paper/main.tex
Updated paper

@@

\subsubsection{Lumpy asteroids}

Finally, we test an asteroid with a discrete change in density distribution (for example, a rock of high density), of the kind that the lumpy model is designed to detect. We place a spherical mass of density six times that of the surrounding medium inside the asymmetric reference asteroid, slightly displaced along $\unit y$. Both the mass and the medium have uniform density. The distributions extracted by the three model for this asteroid are shown in figure \ref{fig:blob-density}.

>>>>

To test the ability of the asteroid to identify discrete changes in density distribution of the kind that the lumpy model is designed to detect, we show one more example extraction. We place a spherical mass of density six times that of the surrounding medium inside the asymmetric reference asteroid, slightly displaced along $\unit y$. Both the mass and the medium have uniform density. The density moments are extracted via  a fit similarly to section \ref{sec:example-fit} and the distributions extracted by the three models for this asteroid are shown in figure \ref{fig:blob-density}.

  % \includegraphics[width=0.3\textwidth]{figs/blob-diff-likelihood.pdf}\hfill
  % \includegraphics[width=0.3\textwidth]{figs/blob-diff-harmonic.pdf}\hfill
  %\includegraphics[width=0.3\textwidth]{figs/blob-diff-lumpy.pdf}

  % \includegraphics[width=0.3\textwidth]{figs/blob-unc-likelihood.pdf}\hfill
  % \includegraphics[width=0.3\textwidth]{figs/blob-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}

  % \includegraphics[width=0.3\textwidth]{figs/blob-ratio-likelihood.pdf}\hfill
  % \includegraphics[width=0.3\textwidth]{figs/blob-ratio-harmonic.pdf}\hfill\hspace{0.3\textwidth}

\jtd{I will also add a discussion of uncertainties once the plots are generated.}

@@
